Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-22 paper/paper.Rmd
various

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs. We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level experimental methods. By a variety of measures, these replications were successful approximately half of the time, providing an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt. We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."

>>>>

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs. We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. The modal outcome was a partial replication, with most yielding weaker evidence than the original study. This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt. We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."
